---
title: 'Milestone #2'
author: "Molly Chiang"
date: "2/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(readxl)
library(janitor)

```

### My Data So Far...

I have added the data file from one of the papers I am considering, "Cerebellar Hemorrhage in Preterm Infants: A Meta-Analysis on Risk Factors and Neurodevelopmental Outcome," to my repo and pushed it to github. I have not done much analysis/investigation of this data as I am still investigating other articles/waiting for a response about the availability of code for this one. 

The repo for this project can be accessed at: https://github.com/mollyechiang/milestone_2


```{r import_data}

# import data from csv saved to my repo
# clean names and label a bunch of placeholder values asNA
# rename two columns and remove unecessary columns

raw <- read.csv("cerebellar_hemorrhage_data.csv") %>%
  clean_names() %>%
  head(25) %>%
  na_if(., "n") %>%
  na_if(., "#VALUE!") %>%
  na_if(., "N") %>%
  na_if(., "-") %>%
  rename("5min_apgar_7_cbh_yes_n" = "x5min_apgar_7_cbh_yes_n", 
        "5min_apgar_7_cbh_no_n" = "x5min_apgar_7_cbh_no_n") %>%
  select(-starts_with("x"))

```

```{r quick_graphic}

raw %>%
  
  # remove one study that had no recored number hospital centers
  
  filter(first_author != "Limperopoulos 2005b") %>%
  
  # select relevant columns and drop rows with any NA's 
  
  select(first_author, total_number_of_infants_study, number_of_centers) %>%
  drop_na() %>%
  
  # plot results w/ a geom col
  # adjust x axis labels and give titles
  
  ggplot(aes(x = first_author, y = total_number_of_infants_study, fill = number_of_centers)) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Number of Infants in Studies for Selected Papers",
         subtitle = "Papers analyzed in 'Cerebellar Hemorrhage in Preterm Infants: A Meta-Analysis \non Risk Factors and Neurodevelopmental Outcome'",
         x = " ",
         y = "Number of Infants",
         fill = "Number of Hospital Centers \n Involved in Study")

```


